|

### 2024-03-19 manuscript/manuscript.qmd
update manuscript

[!Types of Stability and Change](img/StabilityChange.png){#fig-StablityChange fig-alt="Stability & Change Diagram." width="300" height="300" fig-align="left"}

@@

[![Longitudinal Data Analysis Structural Diagram](img/LDAStructure2.png)](https://centerstat.org/resources/)

@@

[!Longitudinal Models/Data Structures](img/Mindmap1copy.png){#fig-LONGmod fig-alt="Longitudinal Models Diagram." width="300" height="300" fig-align="left"}

[![Longitudinal Data Analysis Structural Diagram](img/LDAStructure2.png)](https://centerstat.org/resources/)
<br>

@@

![LDA Table](img/Tabletemp.png)

>>>>

![Types of Stability and Change](img/StabilityChange.png){width=100% #fig-StablityChange fig-alt="Stability & Change Diagram." fig-align="left"}

@@

![Longitudinal Data Analysis Structural Diagram](img/LDAStructure2.png){width=100% #fig-StablityChange fig-alt="Stability & Change Diagram." fig-align="left"}
[Link]((https://centerstat.org/resources/))

@@

![Longitudinal Models/Data Structures](img/Mindmap1.png){width=100% #fig-DataStructures fig-alt="Longitudinal Models & Data Structures" fig-align="left"}

@@

![LDA Table](img/Tabletemp.png){width=100% #fig-LDATable fig-alt="LDA Table" fig-align="left"}
